Supporting Information : Effect of copula on extinction risk

### 2019-02-26 SuppMat.Rmd
verhulst and abrewer with scl=0.6 added

```{r sim_verhulst_scl_1, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"verhulst"
scl<-1

@@

```{r fig_verhulst_scl_1, echo=F, results="hide",cache=T, cache.extra=list(seed,res_verhulst_local,res_verhulst_global)}
pdf(paste(resloc,"verhulst_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

```{r fig_verhulst_extrisk_d0_scl_1, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
verhulst_extrisk_d0<-readRDS(paste(resloc,"verhulst_extrisk_d0.RDS",sep=""))

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model : rc = 1, scl=1) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_verhulst_r_vary_scl_1}](./Results/verhulst_scl_1/verhulst_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model : rc = 1, scl=1) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_verhulst_r_vary_scl_1}](./Results/verhulst_scl_1/verhulst_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model with no dispersion : rc = 1, scl=1); numlocs=5, numsteps=25, numsims=10000\label{fig_verhulst_risk_d0_scl_1}](./Results/verhulst_scl_1/verhulst_extrisk_d0.pdf){ width=40%, height=40% }

@@

```{r sim_abrewer_scl_0.8, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"austinbrewer"
scl<-0.8

@@

```{r fig_abrewer_scl_0.8, echo=F, results="hide",cache=T, cache.extra=list(seed,res_abrewer_local,res_abrewer_global)}
pdf(paste(resloc,"abrewer_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

```{r fig_abrewer_extrisk_d0_scl_0.8, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
abrewer_extrisk_d0<-readRDS(paste(resloc,"abrewer_extrisk_d0.RDS",sep=""))

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Austin Brewer model : K = 50, s = 0.2, rc = 0.02000091, scl=0.8) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_abrewer_r_vary_scl_0.8}](./Results/austinbrewer_scl_0.8/abrewer_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Austin Brewer model : K = 50, s = 0.2, rc = 0.02000091, scl=0.8) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_abrewer_r_vary_scl_0.8}](./Results/austinbrewer_scl_0.8/abrewer_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Austin Brewer model with no dispersion : rc=0.02000091, scl=0.8); numlocs=5, numsteps=25, numsims=10000\label{fig_abrewer_risk_d0_scl_0.8}](./Results/austinbrewer_scl_0.8/abrewer_extrisk_d0.pdf){ width=40%, height=40% }

>>>>

```{r sim_verhulst_scl_0.6, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"verhulst"
scl<-0.6

@@

```{r fig_verhulst_scl_0.6, echo=F, results="hide",cache=T, cache.extra=list(seed,res_verhulst_local,res_verhulst_global)}
pdf(paste(resloc,"verhulst_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

```{r fig_verhulst_extrisk_d0_scl_0.6, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
verhulst_extrisk_d0<-readRDS(paste(resloc,"verhulst_extrisk_d0.RDS",sep=""))

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model : rc = 1, scl=0.6) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_verhulst_r_vary_scl_0.6}](./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model : rc = 1, scl=0.6) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_verhulst_r_vary_scl_0.6}](./Results/verhulst_scl_0.6/verhulst_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model with no dispersion : rc = 1, scl=0.6); numlocs=5, numsteps=25, numsims=10000\label{fig_verhulst_risk_d0_scl_0.6}](./Results/verhulst_scl_0.6/verhulst_extrisk_d0.pdf){ width=40%, height=40% }

@@

```{r sim_abrewer_scl_0.6, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"austinbrewer"
scl<-0.6

@@

```{r fig_abrewer_scl_0.6, echo=F, results="hide",cache=T, cache.extra=list(seed,res_abrewer_local,res_abrewer_global)}
pdf(paste(resloc,"abrewer_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

```{r fig_abrewer_extrisk_d0_scl_0.6, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
abrewer_extrisk_d0<-readRDS(paste(resloc,"abrewer_extrisk_d0.RDS",sep=""))

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Austin Brewer model : K = 50, s = 0.2, rc = 0.02000091, scl=0.6) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_abrewer_r_vary_scl_0.6}](./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Austin Brewer model : K = 50, s = 0.2, rc = 0.02000091, scl=0.6) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_abrewer_r_vary_scl_0.6}](./Results/austinbrewer_scl_0.6/abrewer_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Austin Brewer model with no dispersion : rc=0.02000091, scl=0.6); numlocs=5, numsteps=25, numsims=10000\label{fig_abrewer_risk_d0_scl_0.6}](./Results/austinbrewer_scl_0.6/abrewer_extrisk_d0.pdf){ width=40%, height=40% }
